\thesistitle

### 2019-08-25 sections/related_work.tex
Related work

\section{Refactoring Technique for Large Groups of Software Clones}
A thesis by AlWaqfi~\cite{alwaqfi2017refactoring} propose a method for assessing refactorability of clone classes , whereas the previous tools only focus on clone pairs. The author surveys a set of clone detection tools \cite{kamiya2002ccfinder, baxter1999clonedr, jiang2007deckard, cordy2011nicad} and uses a publicly available dataset \cite{tsantalis2015assessing} to measure the amount of clones found by these tools. The resulting data shows that significant portions of source code of the measured systems are cloned. The data also shows that there are large differences between different tools in the amount of clones found. The author also measures of how many clone instances clone classes consist. According to these experiments, about 68\% of clone classes consist of 2 clone instances, 13\% have 3 clone instances, 7\% have 4 clone instances and about 12\% is even larger.

@@

\section{Impact of Clone Refactoring on External Quality Attributes}
A study by Vashisht et al.~\cite{vashisht2018impact} determines the impact of clone refactoring on several quality attributes. They calculate the metrics of the system before refactoring, detect clones using CCFinder \cite{kamiya2002ccfinder}, use JDeodorant to refactor a subset of the detected clones \cite{mazinanian2016jdeodorant} and measure the metrics again after refactoring to assess the impact of the refactoring process on quality attributes. They conclude that some metrics affect some quality attributes positively and some negatively.

In this study, the authors only compare before and after snapshots of refactoring the entire system. This makes it hard to determine why some metrics are negatively influenced.

\section{Clone Recommendation System for Extract Method Refactoring}
Yoshida et al.~\cite{yoshida2019proactive} propose a plugin for the Eclipse IDE that recommends clone refactoring candidates on basis of keystroke tracking. Whenever the user performs the ``Extract Method'' refactoring, the proposed system scans the project for clones that can now use the extracted method. It then shows the developer all places that should be refactored aswell now that a new method has been created. The approach was validated by requesting human participants to apply refactorings to open source systems. On average, it took participants 1,043 seconds to refactor 2.75 clones. They indicate that this is 35\% faster than when working with a popular clone detection tool (GemX).

\section{Effect of clone refactoring on the size of unit test cases}
Badri et al.~\cite{badri2019measuring} measure the impact on clone refactoring on metrics that affect the testability of software. The metrics they measure are size, cyclomatic complexity and coupling. To collect this data, they used two systems that have been de-duplicated manually. They conclude that there is a strong, positive correlation between clone refactoring and the reduction of the size of unit test cases. They also show that code quality attributes that are related to testability are significantly improved.

>>>>

\section{Refactoring Technique for Large Groups of Software Clones}
In a thesis by AlWaqfi~\cite{alwaqfi2017refactoring} the author proposes a method for assessing refactorability of clone classes, whereas most of the previous tools only focus on clone pairs. The author surveys a set of clone detection tools \cite{kamiya2002ccfinder, baxter1999clonedr, jiang2007deckard, cordy2011nicad} and uses a publicly available dataset \cite{tsantalis2015assessing} to measure the amount of clones found by these tools. The resulting data shows that there is a lot of variability in the amount of detected clones between different clone detection tools. The author measures of how many clone instances there are in clone classes. According to these experiments, about 68\% of clone classes consist of 2 clone instances, 13\% have 3 clone instances, 7\% have 4 clone instances and about 12\% is even larger.

@@

\section{Impact of Clone Refactoring on External Quality Attributes}
A study by Vashisht et al.~\cite{vashisht2018impact} determines the impact of clone refactoring on several quality attributes. They calculate the metrics of the system before refactoring, detect clones using CCFinder \cite{kamiya2002ccfinder}, use JDeodorant to refactor a subset of the detected clones \cite{mazinanian2016jdeodorant} and measure the metrics again after refactoring to assess the impact of the refactoring process on quality attributes. They conclude that clone refactoring affects some quality attributes positively and some negatively.

In this study, the authors only compare before- and after-snapshots of refactoring the entire system. This makes it hard to determine why some metrics are negatively influenced. In our study, we consider each separate refactoring, which yields more precise results.

\section{Clone Recommendation System for Extract Method Refactoring}
Yoshida et al.~\cite{yoshida2019proactive} propose a plugin for the Eclipse IDE that recommends clone refactoring candidates on basis of keystroke tracking. Whenever the user performs the ``Extract Method'' refactoring, the proposed system scans the project for clones that can now use the extracted method. It then shows the developer all places that should be refactored aswell now that a new method has been created. The approach was validated by requesting human participants to apply refactorings to open source systems. On average, it took participants 1,043 seconds to refactor 2.75 clones. They report that this is 35\% faster than when working with a popular clone detection tool (GemX).

\section{Effect of clone refactoring on the size of unit test cases}
Badri et al.~\cite{badri2019measuring} measure the impact on clone refactoring on metrics that affect the testability of software. The metrics they measure are size, cyclomatic complexity and coupling. To collect this data, they use two systems that have been de-duplicated manually. They conclude that there is a strong, positive correlation between clone refactoring and the reduction of the size of unit tests. They also show that code quality attributes that are related to testability are significantly improved.
